dplyr and pipes: the basics

### 2018-07-19 content/blog/2014-09-13-dplyr-intro.Rmd
Merge hugo site
Fix typo

---
layout: post
title: "dplyr and pipes: the basics"
subtitle: "Revolutionize your data analysis with dplyr and pipes"
published: true
---

@@

dplyr is [Hadley Wickham's](http://had.co.nz/) re-imagined plyr package (with underlying C++ secret sauce co-written by [Romain Francois](http://blog.r-enthusiasts.com/)). plyr 2.0 if you will. It does less than dplyr, but what it does it does more elegantly and much more quickly.

>>>>

---
title: 'dplyr and pipes: the basics'
subtitle: Revolutionize your data analysis with dplyr and pipes
date: '2014-09-13'
slug: dplyr-intro
---

@@

dplyr is [Hadley Wickham's](http://had.co.nz/) re-imagined plyr package (with underlying C++ secret sauce co-written by [Romain Francois](http://blog.r-enthusiasts.com/)). plyr 2.0 if you will. It does less than plyr, but what it does it does more elegantly and much more quickly.
